I Compensate, therefore I Am \\ (accurate for DNN verification)

### 2024-01-11 Paper/Paper_noProof.tex
fig1
example

A still extremely fast algorithm that aleviates some of this issue is known as {\em DeepPoly} \cite{deeppoly}, also rediscovered as the {\em CROWN} algorithm \cite{crown}. Instead of 
hard bounds, for each neuron $n$ of layer $k$, two affine functions (with input at the previous layer $k-1$) are kept as lower bound and upper bound of the weight of the node.
For instance, $f_i \leq weight(x_i) \leq g_i$ with $f_5(x_3)=f_6(x_4)=0$ and 
$g_5(x_3) = \frac{x_3+2}{2}$,
$g_6(x_4) = \frac{x_4+2}{2}$. 
With that, we get 
$x_7 \leq g_5(x_3) + 2 g_6(x_4) = \frac{x_3 + 2x_4 + 6}{2} = \frac{2x_1 - x_4 + 6}{2}\leq 4.5$.

@@

As far as we know, no formal result states the relationship between the LP approximation and DeepPoly.
We prove now that the LP abstraction is strictly more accurate than the DeepPoly abstraction, as it actually corresponds to considering in DeepPoly both linear functions lower bounding the ReLU function, $ReLU(y) \geq 0$ and $ReLU(y) \geq y$, while DeepPoly considers exactly one.

@@

>>>>

A still extremely fast algorithm that aleviates some of this issue is known as {\em DeepPoly} \cite{deeppoly}, also rediscovered as the {\em CROWN} algorithm \cite{crown}. Instead of 
hard bounds, for each neuron $n$ of layer $k$, two affine functions (with input at the previous layer $k-1$) are kept as lower bound and upper bound of the weight of the node.
For instance, $f_i \leq weight(x_i) \leq g_i$ with $f_5(x_3)=f_6(x_4)=0$ and 
$g_5(x_3) = \frac{x_3+2}{2}$,
$g_6(x_4) = \frac{x_4+2}{2}$. 
With that, we get 
$x_7 \leq g_5(x_3) + 2 g_6(x_4) = \frac{x_3 + 2x_4 + 6}{2} = \frac{3x_1 - x_2 + 6}{2}\leq 5.5$.

@@

As far as we know, no formal result states the relationship between the LP approximation and DeepPoly.
We prove now that the LP abstraction is strictly more accurate tha3 the DeepPoly abstraction, as it actually corresponds to considering in DeepPoly both linear functions lower bounding the ReLU function, $ReLU(y) \geq 0$ and $ReLU(y) \geq y$, while DeepPoly considers exactly one.

@@

Formally, a pair $(\pi,\pi')$ of paths is compensating if:
\begin{itemize}
 \item they have the same starting node $a$ (called {\em source} state) and ending node $b$ (called {\em target} state of $(\pi,\pi')$),
 \item they are disjoints,
 \item the weight $weight(\pi') < 0 < weight(\pi)$.
\end{itemize}

For instance, on Fig.~\ref{fig1}, the paths $\pi= x_2 x_3 x_7$ has weight $1$, while the
path $\pi'= x_2 x_4 x_7$ has weight $-2$, hence $(\pi,\pi')$ is a compensating pair of paths.
We call a path $\pi$ {\em compensating} if there exists a path $\pi'$ such that either $(\pi,\pi')$ or 
$(\pi',\pi)$ is compensating.

Compensating pair of paths will make precision of the target state reduce when using overabstraction of values. Here, $weight(x_7) \leq 4$ (the value is reached for $x_1=1$ and $x_2=-1$). However, Box computes an upper bound of $6$, and while DeepPoly recovers some of the dependency in $x_2$, it can only cancel out some of $x_2$ value due to the ReLU over-abstraction (a contribution of $\frac{-x_2+4}{2} \leq 2.5$ instead of the exact $-x_2 \leq 1.5$), and obtain a bound of $weight(x_7) \leq 5.5$ instead of $4$.

Intuitively, the target state receives the weight from the source state from the different paths from the source to the target. As the weight of the path is opposite, some of this weight will cancel out,
by an amount up to $2 min(|weight(\pi')|,|weight(\pi')|)$. This amount can however be reduced by the ReLU functions, because of clipping by the ReLU function. Assume that the inputs $x_1,x_2$ lies in $[-1,-0]$. Then the weight at $\hat{x_3}$ will be always 0, no matter the input, and there will be no compensation to 
$weight(\pi')$.
